Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-07-30 abstract.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method. For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using the declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e.  $< T_c >$, $k-M$ slope) of the network and dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope. The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences. 
\end{abstract}

>>>>

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method. For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using the declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e.  $< T_c >$, $k-M$ slope) of the network and dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining the results of this study with three similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope. The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences. 
\end{abstract}

### 2016-07-30 introduction.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs. Basically, the visibility graph presents the connection between nodes in a network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other if no other event interrupts their linear connection. In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:

@@

In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph. They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class. According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph. The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014} .   

@@

\citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India. They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary. In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog. Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks. 

@@

In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions, namely Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view.  \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}. Northern Iran has an extensive seismic history.  Having a considerable number of earthquakes and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study, we present the relationship between  $k-M$  slope and $b-value$  in these three different tectonic seismic regions. We also investigate the variation of  $<T_C>$  value through time.

>>>>

\section{Introduction}
\noindent
This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15). \citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs. Basically, the visibility graph presents the connection between nodes in a network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other if no other event interrupts their linear connection. In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:

@@

In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph. They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class. According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph. The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  Using the synthetic seismicity generated by a simple stick-slip system with asperities, \citet{Telesca2014-pone} investigated the relationship between the $b-value$ of the Gutenberg-Richter law and the slope of the $k-M$ plot as obtained by the VG method. They build up a frictional system as a proxy of geological faults under tectonic stress and defined different asperities by means of modifying the sandpaper grade. They collected data after the first run ($R_1$) and the fifth run ($R_5$) mimicking the younger and mature faults, respectively. They calculated the magnitude as a normalized displacement in range of $1-10$. According to their study the $b-value$ and the $k-M$ slope are linearly correlated to each other with a high correlation coefficient.\\

@@

VG method also is applied through considering the timespan between earthquakes. \citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India. They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary. In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog. Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks. 

@@

In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).  Recently, northern Iran has been studied in detail from different seismological points of view.  \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}. Using the smoothed seismicity method, \citet{Khoshnevis2016} studied the seismic hazard of the three northern tectonic seismic regions. Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series. Significant aspect of our work include the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zones. We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions. We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude. We also investigate the variation of  $<T_C>$  value through time.

### 2016-07-30 main.tex
change the reference style to numerical.
fix some problem.
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\documentclass[authoryear,preprint,review,12pt]{elsarticle}

% Packages
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}

% Journal Name
\journal{Physica A}

@@

% Authors
\author[label1]{Naeem Khoshnevis\corref{cor1}}
%\author[label1,label2]{Shima AzizzadehRoodpish}
\cortext[cor1]{Corresponding author. Tel: \\
                  Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}

% Affliations
%\address[label1]{Center for Earthquake Research and Information}
%\address[label2]{Department of Civil Engineering}

@@

\begin{keyword}
Visibility Graph \sep Earthquake sequence \sep Magnitude \sep North Iran \sep b-value

@@

\input{content}
\bibliographystyle{elsarticle-num-names}
\bibliography{VG}

>>>>

%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
\documentclass[a4paper,review]{elsarticle}
% Packages
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}

% Journal Name
\journal{TBD}

@@

% Authors
\author[label1]{Naeem Khoshnevis\corref{cor1}}
\author[label1,label2]{Shima AzizzadehRoodpish}
\author[label1,label2]{Ricardo Taborda}
\author[label3]{Luciano Telesca}
\cortext[cor1]{Corresponding author. Tel: \\
                  Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}

% Affliations
\address[label1]{Center for Earthquake Research and Information, University of Memphis, 3890 Central Ave., Memphis TN 38152, USA}
\address[label2]{Department of Civil Engineering, University of Memphis, 3890 Central Ave., Memphis TN 38152, USA}
\address[label3]{Institute of Methodologies for Environmental Analysis, National Research Council, Tito, Italy}

@@

\begin{keyword}
Visibility Graph \sep Earthquake Sequence \sep Magnitude \sep North Iran \sep b-value

@@

\input{content}
\bibliographystyle{elsarticle-num-names}

\bibliography{VG}

### 2016-07-30 results.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\begin{table}[h]
\centering
\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
\begin{tabular}{ccccc}
Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
\end{tabular}
\label{tab:b_k_m_param}
\end{table}

\noindent
Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.  In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}
 \noindent
We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time. The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}
 \noindent
where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region. The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.  \citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope. Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.  According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes. The minimum size of random windows is 150 events. (Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.). The maximum size is the size of the entire catalog. For each randomly picked magnitude time series,  we estimated $Mc$,  and the  $k-M$  and $b-value$ were calculated. Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables. Although changing the number of events and the threshold magnitude is a slight change, the results are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
\label{fig:random}
\end{figure}

\noindent
The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}. The  $k-M$  slope shows the higher coefficient of variation. The  $k-M$  slope is more dependent on the window size and threshold magnitude than  on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series. 
 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and two other studies of Mexican zones  \citep{Telesca2013}  and Pannonia zones  \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.955), and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
\label{fig:regression}
\end{figure}

\noindent
Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time. Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows. The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window. The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar. In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes. The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
\noindent
\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence. Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area, and the decrease in  $<T_C>$   before a large earthquake is clearly visible.  \citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude. Fig.\ref{fig:tc}  shows the decrement in the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake.}
\label{fig:tc}
\end{figure}

>>>>

\begin{table}[h]
\centering
\caption{Declustered number of earthquakes, seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
\begin{tabular}{ccccc}
Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
\end{tabular}
\label{tab:b_k_m_param}
\end{table}

\noindent
Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions. We categorized magnitudes in small magnitude bins ($\Delta M=0.1$). It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event. In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure06.pdf} 
\caption{ $k-M$ relationship for north Iran tectonic seismic regions. The blue circles indicate the connectivity degrees. The red line is the linear regression line fits the data. The numbers on the lines is the slope of the lines.}
\label{fig:k_m_plot_m}
\end{figure}
 \noindent
We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time. The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}
 \noindent
where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region. The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.  \citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope. Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.  According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes. The minimum size of random windows is 150 events. (Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.). The maximum size is the size of the entire catalog. For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated. Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables. Although changing the number of events and the threshold magnitude is a slight change, the results are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
\label{fig:random}
\end{figure}

\noindent
The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}. The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series. 
 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citet{Telesca2014-pone}. Adding the results of the current study into the results of three previous similar studies improves the regression factor, and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure08.pdf} 
\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}. The lines represent the linear regression fit of data. The correlation coefficients (R) are represented for different combination of data. }
\label{fig:regression}
\end{figure}

\noindent
Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time. Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows. The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window. The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar. In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes. The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
\noindent
\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence. Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area. The reduction of  $<T_C>$   before large earthquakes is clearly visible.  \citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude. Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure09.pdf} 
\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) as a function of time for three tectonic seismic regions in north Iran. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference). Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
\label{fig:tc}
\end{figure}

### 2016-07-30 seismicity.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\section{Tectonic seismic regions and seismicity parameters}
\noindent
Iran is situated over the Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. Based on seismicity parameters, different tectonic seismic divisions have been defined for Iran.  Some studies have defined more detailed divisions \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province  \citep{Stocklin1968,Takin1972,Berberian1976}.  \citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering  \citet{Mirzaei1998}  a division as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is situated in the gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

\noindent
The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. The North Tehran Thrust adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz. The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\ 
\noindent
The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.

The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults, striking roughly E - W  \citep{Berberian2001}.  \citet{Trifonov1978}  reported active displacement along the main Kopeh-Dagh fault for more than 500 km.

@@

\subsection{Declustering} 
\noindent
It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process. Therefore, in order to accomplish this, we declustered the earthquake catalog. In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology  \citep{Gardner1974}. Fig.~\ref{fig:seismicity}  shows the epicenter of declustered instrumental  earthquakes.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure02.pdf} 
\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.}
\label{fig:seismicity}
\end{figure}

\subsection{Catalog Completeness}
\noindent
Catalog completeness is an important factor in studying an earthquake sequence.  In this study, we used the Goodness-of-fit test (GFT) \citep{Wiemer2000} to determine the completeness magnitude. According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}. We increased the minimum magnitude and repeated the process in order to calculate the goodness of fit for each magnitude.  \citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select completeness of the catalog. However,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions. For each tectonic seismic region, we selected the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit greater than 90\%.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
\caption{Goodness of fit value of GFT method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:completeness}
\end{figure}

In this study, we assume the minimum magnitudes for complete recording,  $M_C$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude greater than the completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:mag-time}
\end{figure}

>>>>

\section{Tectonic seismic regions and seismicity parameters}
\noindent
The Iranian plateau is located on the Himalayan-Alpine seismic belt. It has a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eighth century. Based on seismicity parameters and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968,Takin1972,Berberian1976}, and up to twenty to twenty-three tectonic seismic regions in the most elaborate ones \citep[e.g.,][]{Nowroozi1976,Tavakoli1999}. \citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering the devision of  \citet{Mirzaei1998} as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure01.pdf} 
\caption{Region of interest and tectonic seismic regions. At the top, the map of Iran and surrounding countries. The study area is located in the gray box. At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

\noindent
The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. The North Tehran Thrust adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz. The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\ 
\noindent
The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
\noindent
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults, striking roughly E - W  \citep{Berberian2001}.  \citet{Trifonov1978}  reported active displacement along the main Kopeh-Dagh fault for more than 500 km. Main fault lines and fault systems in the interest region is represented in Fig.~\ref{fig:faults}.

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
\caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
\label{fig:faults}
\end{figure}

@@

\subsection{Declustering} 
\noindent
It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process. Therefore, in order to accomplish this, we decluster the earthquake catalog. In compiling the catalog of events, foreshocks and aftershocks are removed using a declustering methodology  presented by \citet{Gardner1974}. Fig.~\ref{fig:seismicity}  shows the epicenter of declustered instrumental  earthquakes.

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran. Different colors indicate the seismicity of different regions. Size of symbols are proportional to the magnitude of the events.}
\label{fig:seismicity}
\end{figure}

\subsection{Catalog Completeness}
\noindent
Catalog completeness is an important factor in studying an earthquake sequence. This characteristic measured as the minimum magnitude of complete recording for earthquake catalog . The completeness magnitude $(M_c)$ is often determined using simple numerical analysis. Two common approaches are maximum curvature method and (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}). We use the Goodness-of-fit test and compute $M_c$ for each region's catalog. According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}. We increase the minimum magnitude and repeate the process in order to calculate the goodness of fit for each magnitude.  \citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog. However,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions. For each tectonic seismic region, we select the magnitude corresponding to the highest goodness of fit or the first magnitude with the goodness of fit greater than 90\%.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure04.pdf} 
\caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period. The symbols indicate the computed GFT values as function of the earthquake magnitude. The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.}
\label{fig:completeness}
\end{figure} 
\noindent
Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude greater than the completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure05.pdf} 
\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time. The figure only represents the reclustered events greater than minimum magnitude. The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
\label{fig:mag-time}
\end{figure}
